Chapter 2 Draft

### 2020-04-15 Rmd/Draft.Rmd
Quick comments

*Hypothesis*

@@

3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community? -Hypothesis- communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.

@@

@@

@@

@@

kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", caption = "Metadata for all the different networks/metawebs used at their maximum level of organization (metaweb if possible).") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)
```
\end{landscape}

>>>>

*Hypothesis*
[overall, guay, pero le falta story telling]()

@@

3) Can we predict the diversity of pollinator interactions with the phylogenetic distance of a community? -Hypothesis- communities with a higher number o close related species will likely have trait redundancy and less diversity of interactions.
[IB: Este ultimo punto es interesante, PERO quizas es otro paper? Mirate https://www.nature.com/articles/nature05956 Rezende tiene otros papers al respecto]()

@@

# IB: No me cuadra la cantidad de dipteros (y pocos hymenopteros) en mis redes, recheck colores. Ojo, quizas esta bien, pero me sorprende. 
# IB; Para visitas hay oalgo mal seguro, no hay abejas en 2015 ¿?

@@

## Molaria compararlo con estimas a nivel mundial de que % de plantas son hermafroditas, (y igual para todos los traits). En otras palabras, salen estas porporciones por que reflejan las proporciones generales? O se desvian?)  
```

@@

##Que flipe que al norte hay más self-compatible?! Esto debe estar decrito en la literatura, verdad? Hay una correlación entre la diversidad de abejas y el nivel de self incompatibility?  
```

@@

kable(m, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace", caption = "Metadata for all the different networks/metawebs used at their maximum level of organization (metaweb if possible).") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T)

### en 2008 por que hay 3 networks? Netiendo como puede haver 12, 6 o 2, pero 3? OK entendido, ya veo el 3+3! pon 2008a 2008b?
```
\end{landscape}
